---
title: "Lab 01 - Hello R"
author: "Insert your name here"
date: "Insert date here"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

The datasaurus_dozen dataset has 1846 rows and 3 columns (varaibles). The three variables are (1) dataset 

### Exercise 2
Plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
The scatterplot reveals that the data points form the shape of a dinosaur. 


Calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The Pearson correlation coefficient is approximately r = 0.064, which suggests a strongly weak negative linear relationship between x and y. This indicates that there is no linear relationship between x and y. 

### Exercise 3

Repeat the same analysis for star dataset. 

```{r plot-star}
star <- datasaurus_dozen %>% 
  filter(dataset == "star")

ggplot(data = star, mapping = aes(x = x, y = y)) + 
  geom_point()
```

The scatterplot shows that the data points form a star shape. 

```{r cor-star}
star %>% 
  summarise(r = cor(x, y))
```
The Pearson correlation coefficient is approximately r = 0.063, which suggests a strongly weak negative linear relationship between x and y. This indicates that there is no linear relationship between x and y. 


### Exercise 4

Repeat the same analysis for away dataset. 

```{r plot-away}
away <- datasaurus_dozen %>% 
  filter(dataset == "away")

ggplot(data = away, mapping = aes(x = x, y = y)) + 
  geom_point()
```

```{r cor-away}
away %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Visualize all 13 datasets at once using faceting to see how different they look 

```{r plot-all-datasets}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) + 
  geom_point() + 
  facet_wrap(~dataset, ncol = 4) + 
  theme(legend.position = "none")
```
```{r cor-all-datasets}
library(knitr)
datasaurus_dozen %>% 
  group_by(dataset) %>% 
  summarise(r = cor(x, y)) %>% 
  knitr::kable(digits = 3, caption = "Correlation between x and y for all datasets")
```

